A Case Study in Preserving a High Energy Physics Application

### 2014-03-01 paper.tex
add JCDL references

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        Ntuples data    & hdfs & 24TB & 43.3GB & 20GB \\ \hline
        CMSSW binaries     & local & 1.16TB & 448.3MB & 6.3MB\\ \hline
        Tau source       & git & 73.7MB & 73.7MB & 73.7MB \\ \hline
        PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
        .h file       & http & 41KB & 41KB & 41KB \\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
        CVMFS & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        NDCMS & optFS & 862GB & N/A & 53KB \\ \hline
        AFS & AFS &10.2GB & N/A & 34MB\\ \hline
        Total      &    & 181.1TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|r|}
    \hline
    Data Category &Location & Data Size \\ \hline
    HDFS & hadoop &20GB \\ \hline
    PanFS & opt & 1.6MB \\ \hline
    CVMFS & cvmfs &103MB \\ \hline 
    NDCMS & opt &53KB \\ \hline
    AFS & afs &34MB \\ \hline
    Local FS& bin etc lib lib64 sbin tmp usr&68.3MB \\ \hline
    Total & &21GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 4}
    \label{table:datasize-3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
     Data Category & Data Size & Data Size \\
    & Solution 2 & Solution 4\\ \hline
    HDFS & 43.3GB & 20GB \\ \hline
    PanFS & 155TB & 1.6MB \\ \hline
    CVMFS & 7.4GB &103MB \\ \hline
    NDCMS & 862GB &53KB \\ \hline
    AFS & 10.2GB &34MB \\ \hline
    Local FS& 110GB&68.3MB \\ \hline
    Total & 156TB &21GB \\ \hline
    \end{tabular}
    \caption{Data Size Comparison beweeen Solution 2 and 4}
    \label{table:datasize-2nd3rd}
\end{table}

@@

Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing preserved software library has been made. 
\cite{compostella2010cdf} discussed software distribution mechanism over the Grid using Parrot. 
\cite{blomer2011cernvm} proposed CVMFS to facilitate the software distribution over the network to CernVM. 
\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.

\subsection{figure out the absolutely relevant data and software }

@@

\subsection{the importance of case study}
\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation
\cite{matthews2010framework} designed a tool to capture software preservation properties within a software environment through a series of case studies conducted to evaluate the software preservation framework.
\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
To figure out how to preserve HEP applications, this paper studies one case of preserving one representative HEP application.

>>>>

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        Ntuples data    & hdfs & 24TB & 43.3GB & 20GB \\ \hline
        CMSSW binaries     & local & 1.16TB & 448.3MB & 6.3MB\\ \hline
        Tau source       & git & 73.7MB & 73.7MB & 73.7MB \\ \hline
        PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
        .h file       & http & 41KB & 41KB & 41KB \\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
        Cern files & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        NDCMS & NFS & 862GB & N/A & 53KB \\ \hline
        Local store & AFS &10.2GB & N/A & 34MB\\ \hline
        Total      &    & 181.1TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|r|}
    \hline
    Data Category &Location & Data Size \\ \hline
    HDFS & hadoop &20GB \\ \hline
    PanFS & pscratch & 1.6MB \\ \hline
    CVMFS & cvmfs &103MB \\ \hline 
    NFS & opt &53KB \\ \hline
    AFS & afs &34MB \\ \hline
    Local FS& bin etc lib lib64 sbin tmp usr&68.3MB \\ \hline
    Total & &21GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 4}
    \label{table:datasize-3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
     Data Category & Data Size & Data Size \\
    & Solution 2 & Solution 4\\ \hline
    HDFS & 43.3GB & 20GB \\ \hline
    PanFS & 155TB & 1.6MB \\ \hline
    CVMFS & 7.4GB &103MB \\ \hline
    NFS & 862GB &53KB \\ \hline
    AFS & 10.2GB &34MB \\ \hline
    Local FS& 110GB&68.3MB \\ \hline
    Total & 156TB &21GB \\ \hline
    \end{tabular}
    \caption{Data Size Comparison beweeen Solution 2 and 4}
    \label{table:datasize-2nd3rd}
\end{table}

@@

Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing preserved software library has been made. 
\cite{compostella2010cdf} discussed software distribution mechanism over the Grid using Parrot. 
\cite{blomer2011cernvm} proposed CVMFS to facilitate the software distribution over the network to CernVM. 
\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
\cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.
\cite{schoneberg2013scalable} proposed a scalable, distributed and dynamic workflow system for digitization processes.
\cite{subotic2013distributed} proposed a distributed archival network for process-oriented automatic long-term digital preservation.
\subsection{figure out the absolutely relevant data and software }

@@

\subsection{the importance of case study}
\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation
\cite{matthews2010framework} designed a tool to capture software preservation properties within a software environment through a series of case studies conducted to evaluate the software preservation framework.
\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
\cite{borgman2012data} tried to figure out what types of data are most likely to be used and reused, by whom, and for what purposes through two cases studies.
To figure out how to preserve HEP applications, this paper studies one case of preserving one representative HEP application.
